### 2020-06-04 sections/major/major.tex
Proof of 'monotone is a fragment'

Magic is commonly quantified via monotones \nick{CITE}. 
A monotone is a projection from the $d$-dimensional set of density states of the theory to the real line. 
It is monotonically decreasing under free operations, reflecting the no resource generating property of free operations and thus respecting the pre-order $\prec$ of the theory.
A popular magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
However, a single monotone does not provide information on whether two states are incomparable in the theory.
Motivated by this restrictive nature of the monotone, we introduce the idea of a \emph{fragment} as a less restrictive way of comparing the resource of states in an arbitrary theory $\R = (\F, \O)$. \nick{explain exactly why fragments $>$ monotones}
Let $\R' = (\F', \O')$ be a subtheory of $\R$ so that $\F' \subseteq \F$ and $\O' \subseteq \O$. 
Then, we define a fragment as follows.
\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
    We call a resource fragment of $\R$ any theory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$, if there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
    \begin{enumerate}
        \item $\Pis: \F \mapsto \F'$ and $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$ for any states $\rho_1, \rho_2 \in \F$;
        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for any free operations $\E_1, \E_2 \in \O$. 
    \end{enumerate}
    We call $\Pi$ a resource projection.
\end{definition}
The subtheory $\R'$ is essentially the image of the surjection $\Pi$.
The point of constructing a resource fragment with such a surjective map would be to achieve a more convenient set of free states or operations, or importantly a more convenient pre-order.

@@

Any monotone is a trivial example of a resource fragment in the sense of the following~\cref{thm:monofrag}.
\begin{proposition}\label{thm:monofrag}
	Any monotone $\cal{M}$ of a resource theory $\R$ is a resource projection that maps the set of free states to $0$ and the pre-order $\prec_\R$ to a total order.
\end{proposition}
\begin{proof}
	Trivial.
\end{proof}
Mapping free states to real numbers and free operations to simple addition, the two conditions in the definition are equivalent to monotonicity and additivity respectively.
The ``free state'' for real numbers is 0 and all free states of the resource theory are mapped onto it.

@@

\begin{proposition}
    A state conversion $\rho \xrightarrow{\E \in \O} \tau$ is possible only if there exists a free state $\sigma$ such that for \nick{an infinitesimal $\epsilon$}, $\W{\tau} \prec_{\W{\sigma'}} \W{\rho}$, where $\sigma' = (1-\epsilon)\sigma + \epsilon \frac{1}{d}\id$.
\end{proposition}

@@

\begin{figure}
    \centering
        \includegraphics[scale=0.5]{sections/major/operations.pdf}
    \caption{Zoo of allowed operations for magic resource theories.
    Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \cpwp$.
    We introduce fragments $\O_\sigma \subset \stochw,\ \sigma \in \F$ that cover $\cpwp$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
    \nick{fragments are the intersections of blue and orange, not the whole bubble - technically $\stochw$ should be replaced by its operational pre-image.}
    }
    \label{fig:zoo}
\end{figure}

>>>>

Magic is commonly quantified via monotones \nick{CITE}. 
A monotone is a projection from the $d$-dimensional set of density states of the theory to the real line. 
It is monotonically decreasing under free operations, 
\begin{equation}\label{eq:monotonicity}
    \cal{M}(\rho_1) \leq \cal{M}(\rho_2)\ \text{if}\ \rho_1 \prec_{\R} \rho_2,
\end{equation}
reflecting the no resource generating property of free operations and thus respecting the pre-order $\prec$ of the theory.
A popular magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
However, a single monotone does not provide information on whether two states are incomparable in the theory.
Motivated by this restrictive nature of the monotone, we introduce the idea of a \emph{fragment} as a less restrictive way of comparing the resource of states in an arbitrary theory $\R = (\F, \O)$. \nick{explain exactly why fragments $>$ monotones}
Let $\R' = (\F', \O')$ be a subtheory of $\R$ so that $\F' \subseteq \F$ and $\O' \subseteq \O$. 
Then, we define a fragment as follows.
\begin{definition}[\textbf{Resource projection}]\label{def:fragment}
    Let a resource theory $\R = (\F, \O)$ have pre-order $\prec_{\R}$ and operational composition rule $\circ_{\R}$. 
    We call a resource fragment of $\R$ any theory $\R' = (\F', \O')$ with pre-order $\prec_{\R'}$ and operational composition rule $\circ_{\R'}$, if there exists a surjective projection $\Pi \equiv (\Pis, \Pio): \R \mapsto \R'$ that satisfies the following two conditions.
    \begin{enumerate}
        \item $\Pis: \F \mapsto \F'$ and $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$ whenever $\rho_1 \prec_{\R} \rho_2$ for any states $\rho_1, \rho_2 \in \F$;
        \item $\Pio: \O \mapsto \O'$ and $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$ for any free operations $\E_1, \E_2 \in \O$. 
    \end{enumerate}
    We call $\Pi$ a resource projection.
\end{definition}
The subtheory $\R'$ is essentially the image of the surjection $\Pi$.
The point of constructing a resource fragment with such a surjective map would be to achieve a more convenient set of free states or operations, or importantly a more convenient pre-order.

@@

Any monotone is a trivial example of a resource fragment in the sense of the following~\cref{thm:monofrag}.
\begin{proposition}\label{thm:monofrag}
	Any monotone $\cal{M}$ of a resource theory $\R$ is a resource projection that maps the set of free states to $0$ and the pre-order $\prec_\R$ to a total order.
\end{proposition}
\begin{proof}
	Consider a monotone $\cal{M}$ in the context of a general resource theory $\R = (\F, \O)$.
	Let $\R' = (\F', \O')$, where $\F' \equiv \mathbb{R}_{\geq 0}$ is the set of non-negative real numbers and $\O'$ is the set of non-increasing real functions mapping $\mathbb{R}_{\geq 0}$ to $\mathbb{R}_{\geq 0}$. 
	Naturally, we also set $\prec_{\R'}$ as the usual total order $\leq$ and $\circ_{\R'}$ as the usual function composition.

	The defining property of a monotone, given in~\cref{eq:monotonicity} ensures condition 1 of~\cref{def:fragment}.

	We can then project any $\E \in \O$ onto a function $f \in \O'$, so that $f$ maps $\cal{M}(\rho)$ onto $\cal{M}(\E(\rho))$ for all states $\rho$.

	\nick{expand}
\end{proof}
Mapping free states to real numbers and free operations to simple addition, the two conditions in the definition are equivalent to monotonicity and additivity respectively.
The ``free state'' for real numbers is 0 and all free states of the resource theory are mapped onto it.

@@

\begin{proposition}
    Let $\R = (\O, \F)$ be a theory of magic.
    If the state conversion $\rho \xrightarrow{\O} \tau$ is possible, then there exists a full-rank free state $\sigma \in \F$ such that $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
\end{proposition}
\begin{proof}
    Suppose there exists $\E \in \O$ such that $\E(\rho) = \tau$.
    The free operation belongs to a $\sigma$-fragment, $\E \in \O_\sigma$, for some $\sigma \in \F$.
    Then, $\W{\E}\W{\rho} = \W{\tau}$ with $\W{\E} \in \stochw$, or, equivalently, $\W{\tau} \prec_{\W{\sigma}} \W{\rho}$.
\end{proof}
\nick{This proposition needs modification. What about $\E(\rho) = \ketbra{0}$?}

@@

\begin{figure}[b]
    \centering
        \includegraphics[scale=0.45]{sections/major/operations.pdf}
    \caption{Zoo of allowed operations for magic resource theories.
    Established theories involve operations within the yellow regions, following the hierarchy $\so \subset \cspo \subset \spo \subset \cpwp$.
    We introduce fragments $\O_\sigma \subset \stochw,\ \sigma \in \F$ that cover $\cpwp$ with each one extending to a set of stochastic maps that allows for $\bmd$-majorization to be used.
    \nick{fragments are the intersections of blue and orange, not the whole bubble - technically $\stochw$ should be replaced by its operational pre-image.}
    }
    \label{fig:zoo}
\end{figure}
